Local Group Satellite Distributions in the Illustris Simulation

### 2017-10-07 paper/paper.tex
+1 paragraph

We build two different kinds of statistics from these satellites
First, we compute the shape and alignments for a varying number of
satellites $11\leq N_{s}\leq 15$ keeping their ranking in
$M_V$ or $V_{max}$. 
This allows us to estimate the variation expected by changing the
satellite number. 
The second kind of statistics are computed for a fixed number of
satellites $N_{s}=11$ randomly selected from the top $15$ ranked
satellites. 
We perform this bootstrapping $10$ times for each pair. 
This allows us to estimate the variation expected by randomly sampling
the satellites from a parent distribution.

@@

The lower left panel re-inforce the picture of a highly structured
MW. 
It corresponds to the $c/a$ ratio and shows the same trends observed
in for the plane width. 
First, the ratio is lower for the MW than it is for M31; second, the
ratio for the MW is also lower than the expectation for the randomized
sample while the results for M31 is within the expectations from \rand.  
In this case the median value of the \rand\ distributions follow the
$1:1$ line as expected.
The lower right panel does not show any surprises. 
All the distributions from \rank, \boot\ and \rand\ are consistent
both for the MW and M31.

>>>>

We build two different kinds of statistics from these satellites
First, we compute the shape and alignments for a varying number of
satellites $11\leq N_{s}\leq 15$ keeping their ranking in
$M_V$ or $V_{max}$. 
This allows us to estimate the variation expected by changing the
satellite number. 
The second kind of statistics are computed for a fixed number of
satellites $N_{s}=11$ randomly selected from the top $15$ ranked
satellites. 
We perform this bootstrapping $5$ times for each pair. 
This allows us to estimate the variation expected by randomly sampling
the satellites from a parent distribution.

@@

The lower left panel re-inforces the picture of a highly structured
MW. 
It corresponds to the $c/a$ ratio and shows the same trends observed
in for the plane width. 
First, the ratio is lower for the MW than it is for M31; second, the
ratio for the MW is also lower than the expectation for the randomized
sample while the results for M31 is within the expectations from \rand.  
In this case the median value of the \rand\ distributions follow the
$1:1$ line as expected.
The lower right panel does not show any surprises. 
All the distributions from \rank, \boot\ and \rand\ are consistent
both for the MW and M31.

We can quantify the degree at which the observed satellite distributions are 
different from their spherically randomized counterparts.
Figure \ref{fig:lg_distributions} shows the probability distributions
from the \rand\ pairs with an overplot of the LG values.
The upper left panel shows the power law distribution for $\mu$. The
results are not perfectly horizontal because the optimal power value
$\hat{alpha}$ is slightly different from $1$, the uncertainties in
this value are naturally consistent with the unit value expected for
an homogeneous distribution. 
In this case all values are equiprobable.
In the case of the $b/a$ ratio (lower right panel) both the MW and M31
are consistent with the \rand\ distribution.

For all the other cases the Milky Way
